### 2009-12-01 docs/marcello-dissertation/thesis/preamble.tex
Updates to the abstract
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@665 559edde2-a4d4-44e0-96fc-4035e40d7396

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Abstract goes here
}

>>>>

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Sensor Networks are becoming more and more important to different science
communities bacause of what it produces: the raw data for different studies.
In order to make use the collected data, researchers may have to dissect the
characteristics of the sensor network in question, regarding different
properties such as the purpose and location of the observed data, as well as
how the data is described. In this way, this work first proposes a set of
taxonomies that can be used to study and classify a given instance of sensor
network and its produced data. Then, based on the classes of these taxonomies, 
this work selected a Document-Oriented Database system as a result of an
empirical evaluation of the requirements for a new persistence layer for 
NetBEAMS, the case study used in this work. For this reason, the design and
implementation of a new data persistence component for NetBEAMS show how
schema-less data models help decreasing the complexity related to the database
layer, not yet reported by the state of the art. Furthermore, this work also
proposes the use of Database Shards in order support the implementation of
Data-Centric sensor networks. 
}
\vspace*{\fill}
